\noindent \textsc{It was}\poeticmarginnote{\frakturish Das Schloß} about four o'clock when we arrived. The fields lay deep in fog. The tarmac of the avenue sped quietly beneath us, marbled with oilslicks and rainwater. It was Edwardian apparently, the house -- all pale stone and subtle volutes. Suzy came out to meet us on the front steps. Her expression was warm, and her hair was a mess.

Then we sat down for tea and cakes. With the big bay window and the grim weather outside, we all felt glad of the fire. I was so nervous, seeing Suzy again after all this time, I lost my appetite, but she wasn't the sort to take offence. Absent friends were toasted. Suzy grilled you excitedly about life back home in Vienna. When we'd finished, you stacked the things up onto the tray, and I carried it out.

In the kitchen, Suzy introduced us to one of the other women, Jess. She must have been half Suzy's age, twice ours -- and yet already there little streaks of grey in her ponytail. She was nice, something of a gentlewoman. She talked in an animated fashion about a faith healing at a recent prayer meeting, emphasising certain points with the knife with which she chopped the onions. I thought how she must have had the lads running after her when she was our age, and wondered if she was married. Then Suzy ushered us into the garden.

Apparently it had been a good year for the jasmine, but it was October now and what hadn't been cut back hung shrivelled and brown. A narrow path ran out across the lawn, down to the river. The cherry tree was full of droplets of rain. Through a plastic window, the shelves of the tool shed presented arms: the tines and blades properly oiled and stacked. I said to myself, It'd be good to find work here, over the spring. Then we came in out of the cold.

A long windowed corridor separated the kitchen from the chapel: a handsome room, oak-panelled and oak-floored, with bean bags spread around the altar. In place of a cross there was a painting of the crucifixion, almost like a photograph. His eyes were bulging, bones visibly broken, the hair on his chest matted with blood. I remembered a passage Suzy had given me on a piece of card during our first acquaintance -- `Christ\poeticmarginnote{Sta Teresa de \'Avila} has no body on earth now but yours' -- then I looked at you. You didn't seem to pay any of it much attention, but perhaps you just kept your eyes lowered out of respect. I find you very hard to read sometimes, and that gets to me.

After that, Suzy took us upstairs to another room. It was as big as the lounge and similarly furnished, but the chairs were laid out in a more formal circle. Suzy said that everyone gathered here every day, first thing in the morning and after supper. In the evenings, the women might want to say sorry for the sins of the day, or tell stories about the things that had happened to them in their lives. There was never any pressure to speak though, she said, nothing to worry about.

There was a library just across the landing: a gorgeous space with a thick red carpet and a stone fireplace. There were eight mahogany bookshelves protruding from the walls, four on the left and four on the right. Then in the centre space, beneath the window, was an enormous copy of \emph{Pilgrim's Progress} laid open on a lectern. The binding had been carved out of a rich red leather, and inside were the most intricate woodcuts: Apollyon was there with all his teeth and fish scales, and Discretion with suitably come-hither eyes. I called you over and asked if you'd ever read it. You said you tried once when you were fourteen, but it didn't really work in your language.

Then Suzy led us up the final set of stairs, to where the bedrooms were. Near the gable end she showed you into the place that had been chosen for you. It was fairly bare: a small wardrobe, a desk and a bed, the walls painted matt magnolia. I placed your holdall on the duvet and began to unpack: your jeans and t-shirts, bras and underwear, your blue silk dress, your Bible. The window looked out onto the garden and over into the valley beyond: the moor and husks of industry. Everything was black or gold -- except the river, which was silver -- the sun being stayed an inch over the col.

Suzy said to me, `You'd best be going now. I wish I could let you stay the night, but really I'm breaking the rules just having you here now.' And you looked at me like we were the last two people left in the world, like the cripple at the Beautiful Gate. We hugged tenderly, awkwardly.

`Don't worry,' I said. `I'll be back in a couple of weeks.'

\prosesep

Moreover, there were two blond women drinking Campari at a small table in the far corner of the taproom. I raised my eyebrows; you consented; they seemed happy enough to be chatted to, and so the four of us sat down together round the same board. They both looked about thirty years old, with that slackness in the flesh -- here barely perceptible -- that a woman can't help but acquire after her second or third child; and they were dressed shabbily, although it was clear they were wearing their best clothes. The conversation went well; it was awkward, but all parties were eager to get on, and we were both happy to bring the two of them drink after drink.

Later, they were sat on the sofa of our living room; you were laid back in the armchair opposite, and there was I stood in the middle. Then the larger of the two -- that is, the taller -- quickly stripped naked and, leaning back on the cushions, put two fingers inside herself. I pulled her up by her right hand and hugged her close to me. She seemed tiny now; my forearm easily spanned the width of her shoulders, and she was bony -- not emaciated, but quite thin. Meanwhile the other woman had stripped herself too. I felt the weight of my joy in the back of my throat. I wanted both of them. Then the taller one knelt down and pulled down my shorts, and all could see that I was already well hard.

I picked her up and laid her back on the sofa. I knelt between her legs and, with your permission, entered her -- quite forcefully, although she showed no sign of discomfort or distress. Now how can I describe the innermost texture of any woman? All I can say is, it was sweet.
